InformatiCup 2024 Ctrl-Alt-Defeat

### 2024-01-29 paper.tex
Reset citation to iriginal one
Co-authored-by: EhrenbruderRoschtbraten <81183139+EhrenbruderRoschtbraten@users.noreply.github.com>

\cite{radford2018improving} try to avoid this problem in a simple two step procedure:

@@

Another AI generated image detector model is \textbf{Is It AI?} developed by Is It AI. The tool first determines different features of the image, e.g. colour patterns, shapes and textures. These features are determined using machine learning models. Afterwards, the patterns are compared to those, typically contained in human- or AI-generated content. The Is It AI-model was trained on large datasets of human- and AI-generated content to receive the base patterns to compare to. \cite{IsItAI2024}

There is also an AI-generated-image-detection-approach from Content at Scale. They published their \textbf{Advanced AI Image Detector} as a web tool to detect generated AI images. The application categorizes the input content by evaluating pixels, smoothness and other AI image patterns. \cite{ContentAtScale2024Advanced}

>>>>

\cite{radford2019language} try to avoid this problem in a simple two step procedure:

@@
